---
title: "Assignment 3"
author: Bheshta Shahim
format: 
  html: 
    theme: "yeti" 
---

### Choose one of the six charts from murrell01.R and explain how it is configured by adding documentation to the codes. 

```{r,echo=FALSE, warning=FALSE, message=FALSE}
# Piechart
par(mar=c(0, 2, 1, 2), xpd=FALSE, cex=0.5)
pie.sales <- c(0.12, 0.3, 0.26, 0.16, 0.04, 0.12)
names(pie.sales) <- c("Blueberry", "Cherry",
                      "Apple", "Boston Cream", "Other", "Vanilla")
pie(pie.sales, col = gray(seq(0.3,1.0,length=6))) 
```

In this pie chart from murrell01.R, the chart is configured by specifications of parameters, categories, colors, and more. For example, par(mar=c(0, 2, 1, 2), xpd=FALSE, cex=0.5) indicate the positioning, size, and appearance of the pie chart. The names of the categories in the chart are given by the names(pie.sales) part of the code, while the colors are specified by col=gray. 

### Compare the regression models in anscombe01.R, and compare different ways to create the plots. 

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
## Fancy version (per help file)

ff <- y ~ x
mods <- setNames(as.list(1:4), paste0("lm", 1:4))

# Plot using for loop
for(i in 1:4) {
  ff[2:3] <- lapply(paste0(c("y","x"), i), as.name)
  ## or   ff[[2]] <- as.name(paste0("y", i))
  ##      ff[[3]] <- as.name(paste0("x", i))
  mods[[i]] <- lmi <- lm(ff, data = anscombe)
  print(anova(lmi))
}

sapply(mods, coef)  # Note the use of this function
lapply(mods, function(fm) coef(summary(fm)))

# Preparing for the plots
op <- par(mfrow = c(2, 2), mar = 0.1+c(4,4,1,1), oma =  c(0, 0, 2, 0))

# Plot charts using for loop
for(i in 1:4) {
  ff[2:3] <- lapply(paste0(c("y","x"), i), as.name)
  plot(ff, data = anscombe, col = "red", pch = 21, bg = "orange", cex = 1.2,
       xlim = c(3, 19), ylim = c(3, 13))
  abline(mods[[i]], col = "blue")
}
mtext("Anscombe's 4 Regression data sets", outer = TRUE, cex = 1.5)
par(op)

```
Here we can see the four regression data sets given by anscombe01.R; currently, these regression models are uniform, with the same colors and same style. However, we can customize these charts in different ways by changing features such as the line type and color as well as the point color, shape, or size. 
For example, we can change the point type from filled to unfilled or change the color to green or purple. We can also make changes to the line - a dotted line, a traced line, or making the line thicker or thinner. 


### Can you finetune the charts without using other packages? 
####       a) use a serif font 

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
## Fancy version (per help file)

ff <- y ~ x
mods <- setNames(as.list(1:4), paste0("lm", 1:4))

# Plot using for loop
for(i in 1:4) {
  ff[2:3] <- lapply(paste0(c("y","x"), i), as.name)
  ## or   ff[[2]] <- as.name(paste0("y", i))
  ##      ff[[3]] <- as.name(paste0("x", i))
  mods[[i]] <- lmi <- lm(ff, data = anscombe)
  print(anova(lmi))
}

sapply(mods, coef)  # Note the use of this function
lapply(mods, function(fm) coef(summary(fm)))

# Preparing for the plots
op <- par(mfrow = c(2, 2), mar = 0.1+c(4,4,1,1), oma =  c(0, 0, 2, 0), family = "serif")

# Plot charts using for loop
for(i in 1:4) {
  ff[2:3] <- lapply(paste0(c("y","x"), i), as.name)
  plot(ff, data = anscombe, col = "red", pch = 21, bg = "orange", cex = 1.2,
       xlim = c(3, 19), ylim = c(3, 13))
  abline(mods[[i]], col = "blue")
}
mtext("Anscombe's 4 Regression data sets", outer = TRUE, cex = 1.5)
par(op)

```

####       b) try non-default colors

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
## Fancy version (per help file)

ff <- y ~ x
mods <- setNames(as.list(1:4), paste0("lm", 1:4))

# Plot using for loop
for(i in 1:4) {
  ff[2:3] <- lapply(paste0(c("y","x"), i), as.name)
  ## or   ff[[2]] <- as.name(paste0("y", i))
  ##      ff[[3]] <- as.name(paste0("x", i))
  mods[[i]] <- lmi <- lm(ff, data = anscombe)
  print(anova(lmi))
}

sapply(mods, coef)  # Note the use of this function
lapply(mods, function(fm) coef(summary(fm)))

# Preparing for the plots
op <- par(mfrow = c(2, 2), mar = 0.1+c(4,4,1,1), oma =  c(0, 0, 2, 0), family = "serif")

# Plot charts using for loop
for(i in 1:4) {
  ff[2:3] <- lapply(paste0(c("y","x"), i), as.name)
  plot(ff, data = anscombe, col = "maroon4", pch = 21, bg = "palevioletred1", cex = 1.2,
       xlim = c(3, 19), ylim = c(3, 13))
  abline(mods[[i]], col = "skyblue")
}
mtext("Anscombe's 4 Regression data sets", outer = TRUE, cex = 1.5)
par(op)

```

####       c) use own plotting character

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
## Fancy version (per help file)

ff <- y ~ x
mods <- setNames(as.list(1:4), paste0("lm", 1:4))

# Plot using for loop
for(i in 1:4) {
  ff[2:3] <- lapply(paste0(c("y","x"), i), as.name)
  ## or   ff[[2]] <- as.name(paste0("y", i))
  ##      ff[[3]] <- as.name(paste0("x", i))
  mods[[i]] <- lmi <- lm(ff, data = anscombe)
  print(anova(lmi))
}

sapply(mods, coef)  # Note the use of this function
lapply(mods, function(fm) coef(summary(fm)))

# Preparing for the plots
op <- par(mfrow = c(2, 2), mar = 0.1+c(4,4,1,1), oma =  c(0, 0, 2, 0), family = "serif")

# Plot charts using for loop
for(i in 1:4) {
  ff[2:3] <- lapply(paste0(c("y","x"), i), as.name)
  plot(ff, data = anscombe, col = "maroon4", pch = 18, bg = "palevioletred1", cex = 1.2,
       xlim = c(3, 19), ylim = c(3, 13))
  abline(mods[[i]], col = "skyblue")
}
mtext("Anscombe's 4 Regression data sets", outer = TRUE, cex = 1.5)
par(op)

```
### How about using ggplot2? 

```{r, echo=FALSE, warning=FALSE, message=FALSE, results='hide'}
library(ggplot2)
library(gridExtra)  # For arranging multiple plots together
library(grid)      # For adding text grob

# Prepare a list to store ggplot models
anscombe_data <- anscombe

# Create a list to store ggplot objects
plot_list <- list()

# Generate each subset plot
for(i in 1:4) {
  
  # Create a dataframe dynamically for each subset
  df <- data.frame(
    x = anscombe_data[[paste0("x", i)]],
    y = anscombe_data[[paste0("y", i)]]
  )
  
  # Fit a regression model for each subset
  model <- lm(y ~ x, data = df)

  # Create the ggplot for the dataset subset
  p <- ggplot(df, aes(x = x, y = y)) +
    geom_point(color = "maroon4", size = 3) +
    geom_smooth(method = "lm", se = FALSE, color = "skyblue", size = 1.5) +
    labs(title = paste0("Subset ", i)) +
    theme_minimal() +
    theme(text = element_text(family = "serif"))
  
  # Append the plot to the list
  plot_list[[i]] <- p
}

# Create a main title grob
main_title <- textGrob("Anscombe's Four Regression Datasets", gp = gpar(fontsize = 20, fontfamily = "serif"))

# Arrange the plots with gridExtra and add the title
grid.arrange(main_title, 
             do.call("arrangeGrob", c(plot_list, ncol = 2)),
             ncol = 1, heights = c(0.1, 0.9))

```

### Hackathon 
#### Replicate given the Scatterplot matrix displaying COVID-19 deaths in Europe. 

